Summary Tables

### 2020-03-06 summary_tables_outcomes.Rmd
Add missing library tidyr

```{r setup, include=FALSE}
library(knitr)
library(pracma)
library(summarytools)
library(dplyr)
library(purrr)
library(DT)
library(ggplot2)
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, message = F, warning = F, results='asis')

>>>>

```{r setup, include=FALSE}
library(knitr)
library(pracma)
library(summarytools)
library(dplyr)
library(purrr)
library(DT)
library(ggplot2)
library(tidyr)
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, message = F, warning = F, results='asis')
